---
title: "Curso1"
author: "Jorge L."
date: "9/8/2021"
output: html_document
---

My first Homework
======================================

This is a firts R Markdown, to the course Reproducible Research in Coursera

Cherger the libraries
```{r}
library(dplyr)
library(ggplot2)
```
## Loading and preprocessing the data

```{r}
data_raw<-read.csv("/Users/jorgelimas/Documents/MOOCs/COURSERA/Data Science (Specialized) -The John Hopkins University/5. Reproducible Research/activity.csv",sep=",")
data_raw$date<-as.Date(data_raw$date)
View(data_raw)
```

## What is mean total number of steps taken per day?

Histogram

```{r}
data_raw_2<-data_raw %>% group_by(date) %>% summarise(steps_sum=sum(steps))
hist_data<-ggplot(data_raw_2,aes(x=steps_sum))+geom_histogram(bins = 7)+labs(title="Histogram of steps for day")
hist_data                  
```

Mean and Median of steps for day
```{r cars}
data_3<-data_raw %>% group_by(date) %>% summarise(mean=mean(steps),median=median(steps))
data_3
```
Summary of steps total data
```{r}
summary(data_raw$steps)
```

## What is the average daily activity pattern?
Time series plot of the average number of steps taken
````{r}

data_4<-aggregate(x=list(mean=data_raw$steps), by=list(interval=data_raw$interval), FUN=mean, na.rm=TRUE)
ggplot(data_4,aes(x=interval,y=mean))+geom_line()+labs(title="Average number of steps taken")
`````
The 5-minute interval that, on average, contains the maximum number of steps

```{r}
as.data.frame(data_4) %>% select(interval,mean) %>%filter(mean==max(data_4$mean))
```

## Imputing missing values
Code to describe and show a strategy for imputing missing data
```{r}
sum(is.na(data_raw$steps))
```

Replace missing values
```{r}
new_column<-ifelse(is.na(data_raw$steps)=="TRUE",0,data_raw$steps)
```
New dataframe
```{r}
new_data_frame<- data_raw %>% mutate(steps=new_column)
rbind(head(new_data_frame),tail(new_data_frame))
```

Create the new data with total steps

```{r}
steps_total <- data_raw %>% group_by(date) %>% summarise(total=sum(steps))
head(steps_total)
ggplot(steps_total, aes(x=total))+geom_histogram(bins = 7)+labs(title="Histogram de full steps")
```

```{r}
summary(steps_total$total)
```


## Are there differences in activity patterns between weekdays and weekends?
```{r}
data_6<-data_raw %>% mutate(week_day=ifelse(weekdays(data_raw$date)=="Saturday" |weekdays(data_raw$date)=="Sunday","weekend","weekday"))
week_data<-aggregate(steps~ interval+week_day, data_6, mean)
head(week_data)
```

```{r}
ggplot(week_data,aes(x=interval,y=steps,group=week_day))+geom_line()+facet_grid(week_day ~.)
```
